\documentclass{fancycv}

\usepackage{fontspec}
\usepackage{pbox}

\setmainfont[
	Path = fonts/,
	UprightFont = *-regular,
	BoldFont = *-semibold]
{bitter}
\newfontface\slimjim{bitter-light.ttf}[Path = fonts/]
\newfontface\heads{Bebas Neue}

\newlength{\sidebarwidth}
\setlength{\sidebarwidth}{5.2cm}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

\pbox{0.7\textwidth}{
{\fontsize{60}{75}\heads Sam Bell}\\
{\fontsize{32}{34}\heads Biomodeler}}\hfill\pbox{0.3\textwidth}{
\slimjim Val-de-Marne, France.\\
+33~6~10~76~79~48\\
sambell912@gmail.com}

\vspace{0.7cm}

\raggedright Theoretical biophysicist specialised in stochastic systems and critical phenomena. Strong ability to translate problems into mathematical models, investigate these models, and communicate the results to a wider audience.

\vspace{1cm}

\begin{minipage}[t]{\sidebarwidth}
{\fontsize{32}{40}\fontspec{Bebas Neue} Skills}

\vspace{12cm}

{{\fontsize{32}{40}\fontspec{Bebas Neue} Languages}

\vspace{0.7cm}

\raggedright \textbf{English} \hfill {\slimjim Native speaker}\\
\vspace{0.5cm}
\raggedright \textbf{French} \hfill {\slimjim B2/C1}\\
\vspace{0.5cm}
\raggedright \textbf{Spanish} \hfill {\slimjim \pbox[t]{0.7\sidebarwidth}{\raggedleft Semi-professional proficiency}}
}
\end{minipage}\hspace{1.5cm}\begin{minipage}[t]{10.5cm}\setlength{\parskip}{0.5em}
{\fontsize{32}{40}\fontspec{Bebas Neue} Experience}

\vspace{0.7cm}

\textbf{Post-doctoral researcher},\hfill Jun 2019--Present\\
{\slimjim Institut Curie, Paris, France.}

Working on models of active matter and critical phenomena, specifically for the influence of external fields on epithelial monolayers.

Let's try another paragraph and see if this one works or not.

\vspace{0.7cm}

\textbf{PhD, Activation problems in biology},\hfill Oct 2015--Jun 2019\\
{\slimjim Cavendish Laboratory, University of Cambridge, UK.}

\begin{enumerate}
\item Published 8 research papers
\item What else did I do?
\end{enumerate}

\vspace{7cm}

{\fontsize{32}{40}\fontspec{Bebas Neue} Education}

\vspace{0.7cm}

\textbf{MSci, Experimental \& Theoretical Physics},\hfill Oct 2014--Jun 2015\\
{\slimjim Trinity College, University of Cambridge, UK.}

\vspace{0.7cm}

\textbf{BA, Natural Sciences (ETP)},\hfill Oct 2011--Jun 2014\\
{\slimjim Trinity College, University of Cambridge, UK.}
\end{minipage}\\

\end{document}